### 2019-10-31 cv_chanwcom/cv_chanwcom.tex
Update the CV
update the cv

\newcommand*{\ac}[1]{\mbox{#1}}
\tolerance=600
\begin{document}
\begin{flushright}
  {\footnotesize \it    Curriculum Vitae-Chanwoo Kim}
\end{flushright}
%
\section*{\filleft \LARGE \it  \href{https://scholar.google.com/citations?user=pJoZXxYAAAAJ&hl=en}{Chanwoo Kim} \filleft}
\lineunder
{  \it
56 Seongchon-Gil, Seoul R \& D campus, Seocho-gu, Seoul, 06765, South Korea \\
Cell: +82-10-4043-3996, E-mail:
\href{mailto:chanw.com@samsung.com}{chanw.com@samsung.com} \\ \\
Profile Page at Google Research : \href{https://research.google.com/pubs/105202.html}
  {\url{https://research.google.com/pubs/105202.html}} \\ \\
Google Scholar page : \href{https://scholar.google.com/citations?user=pJoZXxYAAAAJ&hl=en}
  {Link to the page} {\color{red} (h-index :22, citations: 1616)} \\ \\
Personal homepage: \href{
  http://www.cs.cmu.edu/~chanwook}{\url{http://www.cs.cmu.edu/~chanwook}}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
% 2019
\nociteintconf{d_gowda_interspeech_2019_00}
\nociteintconf{c_kim_interspeech_2019_00}
\nociteintconf{a_menon_icassp_2019_00}

% 2018 
\nociteintconf{c_kim_interspeech_2018_00}
\nociteintconf{x_zhou_isnn_2018_00},
\nociteintconf{c_kim_icassp_2018_00}
\nociteintconf{c_kim_icassp_2018_01}
%\nociteintconf{r_nongpiur_icassp_2018_00}
%\nociteintconf{a_menon_icassp_2018_00}
% 2017
\nociteintconf{a_menon_asru_2017_00}
\nociteintconf{C_Kim_INTERSPEECH_2017_1}
\nociteintconf{B_Li_INTERSPEECH_2017_1}
\nociteintconf{A_Menon_INTERSPEECH_2017_1}
\nociteintjourn{T_Sainath_IEEETran_2017_1}
\nocitebookchap{T_Sainath_Book_Chapter_2017_1}
% 2016
\nociteintjourn{C_Kim_IEEETran_2016_1}
\nociteintjourn{B_Cho_SigProcLetters_2016_1}

@@

% 2014
\nociteintconf{C_Kim_INTERSPEECH_2014_2}
\nociteintconf{C_Kim_INTERSPEECH_2014_1}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Technical skills
\section*{Technical skills}
\lineunder
\begin{itemize*}
  \item Programming Language :
      C, C++, Pyhon, Perl, Java, Matlab, various shell scripts, etc.
  \item Programming Environments :
      Win32 API, Microsoft Foundation Class (MFC), NumPy/SciPy, MapReduce, and various Linux environments.
  \item Speech Recognition Engine :
      Sphinx, Hidden markov model Tool Kit (HTK), Janus, etc.
  \item Development Tool : Various Linux tools including gcc. Microsoft visual studio,
      Arm Developer Suite (ADS), Code Composer Studio (CCS), etc.
  \item Real-time OS : Rex, Nucleus
\end{itemize*}

>>>>

\newcommand*{\ac}[1]{\mbox{#1}}
\tolerance=600
\begin{document}
\begin{flushright}
  {\footnotesize \it    Curriculum Vitae-Chanwoo Kim}
\end{flushright}
%
\section*{\filleft \LARGE \it  \href{https://scholar.google.com/citations?user=pJoZXxYAAAAJ&hl=en}{Chanwoo Kim} \filleft}
\lineunder
{  \it
56 Seongchon-Gil, Seoul R \& D campus, Seocho-gu, Seoul, 06765, South Korea \\
Cell: +82-10-4043-3996, E-mail:
\href{mailto:chanw.com@samsung.com}{chanw.com@samsung.com} \\ \\
Profile Page at Google Research : \href{https://research.google.com/pubs/105202.html}
  {\url{https://research.google.com/pubs/105202.html}} \\ \\
Google Scholar page : \href{https://scholar.google.com/citations?user=pJoZXxYAAAAJ&hl=en}
  {Link to the page} {\color{red} (h-index :22, citations: 1682)} \\ \\
Personal homepage: \href{
  http://www.cs.cmu.edu/~chanwook}{\url{http://www.cs.cmu.edu/~chanwook}}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
% 2019
\nociteintconf{c_kim_interspeech_2019_00}
\nociteintconf{d_gowda_interspeech_2019_00}
\nociteintconf{a_menon_icassp_2019_00}

% 2018 
\nociteintconf{c_kim_interspeech_2018_00}
\nociteintconf{x_zhou_isnn_2018_00},
\nociteintconf{c_kim_icassp_2018_00}
\nociteintconf{c_kim_icassp_2018_01}

% 2017
\nociteintconf{a_menon_asru_2017_00}
\nociteintconf{C_Kim_INTERSPEECH_2017_1}
\nociteintconf{B_Li_INTERSPEECH_2017_1}
\nociteintconf{A_Menon_INTERSPEECH_2017_1}
\nociteintjourn{T_Sainath_IEEETran_2017_1}
\nocitebookchap{T_Sainath_Book_Chapter_2017_1}
% 2016
\nociteintjourn{C_Kim_IEEETran_2016_1}
\nociteintjourn{B_Cho_SigProcLetters_2016_1}

@@

% 2014
\nociteintconf{C_Kim_INTERSPEECH_2014_2}
\nociteintconf{h_park_interspeech_2014_00}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Technical skills
\section*{Technical skills}
\lineunder
\begin{itemize*}
  \item Machine Learning Toolkits:
      Tensorflow, Keras
  \item Programming Language :
      C, C++, Pyhon, Perl, Java, Matlab, various shell scripts, etc.
  \item Programming Environments :
      Win32 API, Microsoft Foundation Class (MFC), NumPy/SciPy, MapReduce, and various Linux environments.
  \item Speech Recognition Engine :
      Sphinx, Hidden markov model Tool Kit (HTK), Janus, etc.
  \item Development Tool : Various Linux tools including gcc. Microsoft visual studio,
      Arm Developer Suite (ADS), Code Composer Studio (CCS), etc.
  \item Real-time OS : Rex, Nucleus
\end{itemize*}
